### 2021-02-24 paper/fse21/implementation.tex
Substituted "sealed symbolic" to "sealed" by using macro.

\paragraph{Sealed Values.}
The main challenge of implementing dynamic shortcuts is to support sealed
symbolic execution on an existing JavaScript engine.  To represent an abstract
value, we use the \jscode{Proxy} object introduced in ECMAScript 6
(2015, ES6)~\cite{es6}, which allows developers to handle internal behaviors
of specific objects such as property reads and writes and implicit conversions.
We are inspired by \textsc{Mimic}~\cite{mimic}, which used \jscode{Proxy} to
capture accesses from internals of opaque functions.  When the dynamic analyzer
constructs an execution environment at the start of a dynamic shortcut, it
creates \jscode{Proxy} objects to represent abstract values via the
following \jscode{generateSymbol} function:
\begin{lstlisting}[style=myJSstyle]
function generateSymbol() {
  function detect() { /* access detection */ }
  return new Proxy(function() {}, {
    getPrototypeOf: detect,  ...
    construct     : detect
  }); }
var x = generateSymbol();
var y = x;
var z = x + 1;
\end{lstlisting}
The function creates a sealed symbol as a proxy object with a dummy
function object and a handler for all 13 traps using an access detection
function \jscode{detect}.  A sealed symbol invokes the function \jscode{detect}
when any of 13 pre-defined traps are operated on the object, which enables us to
determine whether an object is sealed or not.  For example, the variable
\jscode{y} successfully points to the same symbol stored in \jscode{x}, but the
program invokes the function \jscode{detect} on line 9 because \jscode{x + 1} requires
the actual value of the symbol.  In addition, we instrument unary and binary
operations in Jalangi so that we can detect all the accesses on the
symbol beyond the 13 traps provided by \jscode{Proxy}.
Using this idea, we successfully extended the
JavaScript engine to support sealed symbolic execution.

\paragraph{Synchronization of Control Points.}
For seamless interaction between static analysis and sealed symbolic execution,
synchronization of control points in both worlds is necessary.
The SAFE static analyzer parses a JavaScript program to an Abstract
Syntax Tree (AST), compiles it to its intermediate representation, and
builds a Control Flow Graph (CFG).  It produces annotations for
control points on CFGs including functions, call sites, and object allocation sites.
On the contrary, the Jalangi dynamic analyzer instruments a JavaScript program 
to keep track of necessary information at run time.  Therefore, during
sealed symbolic execution, Jalangi requires the annotations from SAFE to compute
abstract locations of newly created concrete objects and lexical environments.
The key to put annotations on the instrumented code is the source-code
location of the original AST node.  While both CFG of SAFE and
instrumented code of Jalangi maintain the source-code location information,
because they use different parsers we found various location mismatches for corner cases.
Therefore, we synchronize control points of two analyzers by using the closest match
of their source-code locations rather than using their exact match.

\paragraph{Function-Level Dynamic Shortcut.}
The dynamic shortcut is activated when the current abstract state passes the
filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
analysis may suffer from the frequent communication between static and dynamic
analyzers.  To adjust the burden of communication, we only activate new
dynamic shortcut in function entries and deactivate it in the corresponding
function exits thus $\tool$ supports only \textit{function-level} dynamic
shortcut.

\paragraph{Termination.}
To guarantee the termination of static analysis using dynamic shortcuts, the
converter $\asconverter$ should pass an analysis element $(\view, \abselem)$
only when it terminates in a time bound $N$.  Since statically checking the
termination property is a difficult task, we simply perform sealed symbolic
execution with a pre-determined time limit.  When it times out,
we treat it as a failure in conversion;
otherwise, we use the result of sealed symbolic execution.  Our experiments used
5 seconds as the time limit for each sealed symbolic execution.

% \paragraph{Communication between Analyzers.}
% To perform dynamic shortcut, the static analyzer should communicate with the the
% dynamic analyzer by passing the current abstract state and receiving the final
% result of the sealed symbolic execution.  However, The static analyzer SAFE and
% the dynamic analyzer Jalangi are implemented in different languages Scala and
% JavaScript, respectively.  To overcome the difference, we represent abstract
% states as JSON objects and communicate between analyzers by passing them.  For
% each dynamic shortcut, Jalangi constructs the execution environments based on
% the given JSON object and executes the dynamic analysis from the target program
% points.  After finishing the sealed symbolic execution, it sends a newly
% constructed JSON object to SAFE to update the abstract states in the function
% exit point.

%\paragraph{Abstract Locations for Objects.}
%During dynamic analysis, each JavaScript object should be designated by the
%corresponding abstract location used in the static analysis.  In this paper, we
%define abstract locations using the allocation site
%abstraction~\cite{allocation-site} with heap cloning~\cite{heap-cloning} for
%each abstract context in the static analyzer.  Thus, we instrument the given
%JavaScript program to annotate each object created during dynamic analysis with
%its allocation site and context information.  After the sealed symbolic
%execution, the dynamic analyzer collects the objects based on their annotated
%information for each abstract location.

>>>>

\paragraph{{\SealeD} Values.}
The main challenge of implementing dynamic shortcuts is to support {\sealed} execution on an existing JavaScript engine.  To represent an abstract
value, we use the \jscode{Proxy} object introduced in ECMAScript 6
(2015, ES6)~\cite{es6}, which allows developers to handle internal behaviors
of specific objects such as property reads and writes and implicit conversions.
We are inspired by \textsc{Mimic}~\cite{mimic}, which used \jscode{Proxy} to
capture accesses from internals of opaque functions.  When the dynamic analyzer
constructs an execution environment at the start of a dynamic shortcut, it
creates \jscode{Proxy} objects to represent abstract values via the
following \jscode{generateSymbol} function:
\begin{lstlisting}[style=myJSstyle]
function generateSymbol() {
  function detect() { /* access detection */ }
  return new Proxy(function() {}, {
    getPrototypeOf: detect,  ...
    construct     : detect
  }); }
var x = generateSymbol();
var y = x;
var z = x + 1;
\end{lstlisting}
The function creates a sealed symbol as a proxy object with a dummy
function object and a handler for all 13 traps using an access detection
function \jscode{detect}.  A sealed symbol invokes the function \jscode{detect}
when any of 13 pre-defined traps are operated on the object, which enables us to
determine whether an object is sealed or not.  For example, the variable
\jscode{y} successfully points to the same symbol stored in \jscode{x}, but the
program invokes the function \jscode{detect} on line 9 because \jscode{x + 1} requires
the actual value of the symbol.  In addition, we instrument unary and binary
operations in Jalangi so that we can detect all the accesses on the
symbol beyond the 13 traps provided by \jscode{Proxy}.
Using this idea, we successfully extended the
JavaScript engine to support {\sealed} execution.

\paragraph{Synchronization of Control Points.}
For seamless interaction between static analysis and {\sealed} execution,
synchronization of control points in both worlds is necessary.
The SAFE static analyzer parses a JavaScript program to an Abstract
Syntax Tree (AST), compiles it to its intermediate representation, and
builds a Control Flow Graph (CFG).  It produces annotations for
control points on CFGs including functions, call sites, and object allocation sites.
On the contrary, the Jalangi dynamic analyzer instruments a JavaScript program 
to keep track of necessary information at run time.  Therefore, during
{\sealed} execution, Jalangi requires the annotations from SAFE to compute
abstract locations of newly created concrete objects and lexical environments.
The key to put annotations on the instrumented code is the source-code
location of the original AST node.  While both CFG of SAFE and
instrumented code of Jalangi maintain the source-code location information,
because they use different parsers we found various location mismatches for corner cases.
Therefore, we synchronize control points of two analyzers by using the closest match
of their source-code locations rather than using their exact match.

\paragraph{\inred{Function-Level Dynamic Shortcut.}}
\inred{The dynamic shortcut is activated when the current abstract state passes the
filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
analysis may suffer from the frequent communication between static and dynamic
analyzers.  To adjust the burden of communication, we only activate new
dynamic shortcut in function entries and deactivate it in the corresponding
function exits thus $\tool$ supports only \textit{function-level} dynamic
shortcut.}

\paragraph{Termination.}
To guarantee the termination of static analysis using dynamic shortcuts, the
converter $\asconverter$ should pass an analysis element $(\view, \abselem)$
only when it terminates in a time bound $N$.  Since statically checking the
termination property is a difficult task, we simply perform {\sealed}
execution with a pre-determined time limit.  When it times out,
we treat it as a failure in conversion;
otherwise, we use the result of {\sealed} execution.  Our experiments used
5 seconds as the time limit for each {\sealed} execution.

% \paragraph{Communication between Analyzers.}
% To perform dynamic shortcut, the static analyzer should communicate with the the
% dynamic analyzer by passing the current abstract state and receiving the final
% result of the {\sealed} execution.  However, The static analyzer SAFE and
% the dynamic analyzer Jalangi are implemented in different languages Scala and
% JavaScript, respectively.  To overcome the difference, we represent abstract
% states as JSON objects and communicate between analyzers by passing them.  For
% each dynamic shortcut, Jalangi constructs the execution environments based on
% the given JSON object and executes the dynamic analysis from the target program
% points.  After finishing the {\sealed} execution, it sends a newly
% constructed JSON object to SAFE to update the abstract states in the function
% exit point.

%\paragraph{Abstract Locations for Objects.}
%During dynamic analysis, each JavaScript object should be designated by the
%corresponding abstract location used in the static analysis.  In this paper, we
%define abstract locations using the allocation site
%abstraction~\cite{allocation-site} with heap cloning~\cite{heap-cloning} for
%each abstract context in the static analyzer.  Thus, we instrument the given
%JavaScript program to annotate each object created during dynamic analysis with
%its allocation site and context information.  After the {\sealed}
%execution, the dynamic analyzer collects the objects based on their annotated
%information for each abstract location.

### 2021-02-24 paper/fse21/intro.tex
Substituted "sealed symbolic" to "sealed" by using macro.

In this paper, we propose a novel technique to fully utilize
the high performance of dynamic analysis for JavaScript static
analysis in a sound manner by using \textit{dynamic shortcuts}.
During static analysis, one can take a dynamic shortcut, which
consists of three parts: 1) converting the current abstract state to
its corresponding \textit{sealed symbolic state}, 2) performing
\textit{sealed symbolic execution} on the sealed symbolic state, and
3) converting the result of the sealed symbolic execution to its
corresponding abstract state.  Our key observation is that we can use
the fast concrete execution for specific program parts while
preserving the soundness if they do not use abstract values.
For example, consider static analysis of the following code:
\begin{lstlisting}[style=myJSstyle,numbers=none]
    var v = ... // an abstract value
    var obj = { p1: v }, y = "p";
    x = obj[y + 1];
\end{lstlisting}
Because \jscode{y + 1} evaluates to \jscode{"p1"},
the third line assigns the abstract value of \jscode{v} stored in
\jscode{obj.p1} to the variable \jscode{x}.
Note that even though \jscode{obj} contains an abstract value \jscode{v},
because the third line does not ``use'' the value of \jscode{v},
we can concretely execute the code.  Based on this observation,
we introduce sealed symbolic execution, which is concrete execution
using \textit{sealed symbolic values}.  A sealed symbolic value is a
representation of an abstract value in symbolic execution; it signals
the end of the current dynamic shortcut when the sealed symbolic
execution tries to access its value.
To evaluate our technique, we implemented $\tool$ using both SAFE
and Jalangi and analyzed 269 official tests of Lodash 4 library.

>>>>

In this paper, we propose a novel technique to fully utilize
the high performance of dynamic analysis for JavaScript static
analysis in a sound manner by using \textit{dynamic shortcuts}.
During static analysis, one can take a dynamic shortcut, which
consists of three parts: 1) converting the current abstract state to
its corresponding \textit{{\sealed} state}, 2) performing
\textit{{\sealed} execution} on the {\sealed} state, and
3) converting the result of the {\sealed} execution to its
corresponding abstract state.  Our key observation is that we can use
the fast concrete execution for specific program parts while
preserving the soundness if they do not use abstract values.
For example, consider static analysis of the following code:
\begin{lstlisting}[style=myJSstyle,numbers=none]
    var v = ... // an abstract value
    var obj = { p1: v }, y = "p";
    x = obj[y + 1];
\end{lstlisting}
Because \jscode{y + 1} evaluates to \jscode{"p1"},
the third line assigns the abstract value of \jscode{v} stored in
\jscode{obj.p1} to the variable \jscode{x}.
Note that even though \jscode{obj} contains an abstract value \jscode{v},
because the third line does not ``use'' the value of \jscode{v},
we can concretely execute the code.  Based on this observation,
we introduce {\sealed} execution, which is concrete execution
using \textit{{\sealed} values}.  \inred{A {\sealed} value is a symbol
that represent an abstract value in {\sealed} execution}; it signals
the end of the current dynamic shortcut when the {\sealed}
execution tries to access its value.
To evaluate our technique, we implemented $\tool$ using both SAFE
and Jalangi and analyzed 269 official tests of Lodash 4 library.

### 2021-02-24 paper/fse21/javascript.tex
Substituted "sealed symbolic" to "sealed" by using macro.

\section{Dynamic Shortcuts for JavaScript}\label{sec:javascript}
In this section, we introduce the core language of JavaScript that supports
first-class functions, open objects, and first-class property names, and define
sealed symbolic execution of the core language for dynamic shortcuts.
Due to the space limitation, we present the main design of the
language in this paper and refer the interested readers to a companion report~\cite{report}.

@@

\subsection{Sealed Symbolic Execution}

We define the sealed symbolic states by not only extending the concrete values
$\valset$ with symbolic values $\symbset$ but also adding the abstract counters
$\abscountset$ as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
Because JavaScript provides open objects, the properties of objects can be dynamically added or deleted.
Moreover, since object properties are string values that can be constructed at run time,
it is difficult for static analysis to know whether strong updates are possible or not.
To check the possibility of strong updates during sealed symbolic execution,
we augment its states with the abstract counters $\abscountset$.

For each abstract value in a given abstract state,
if the abstract value denotes a single concrete value,
the converter $\asconverter: (\viewset \times
\absdom) \rightarrow (\absimapset \times \symbstset)$
keeps it; otherwise, $\asconverter$ replaces the abstract
value with its unique identifier and maintains the mapping from the
unique identifier to the abstract value to construct an abstract instantiation map.
The opposite converter $\saconverter: (\absimapset \times
  \symbstset)  \rightarrow (\viewset \times \absdom)$
recovers abstract values from their unique identifiers using the abstract instantiation map.
We define the sealed symbolic transition relation $\symbtrans$
only if the next step does not require actual values of any symbolic values.
Otherwise, a given sealed symbolic state does not have any sealed symbolic
transitions to apply.  For example, we add the following rule for the $\kwret$ statement:
\begin{mathpar}
  \inferrule
  {
    \prog(\lab) = \kwret \; \expr\\
    \exprrule{\symbst}{\expr}{\val}\\
    \ctxt(\addr) \in \symbset
  }
  {
    \symbst = (\lab, \mem, \ctxt, \addr, \abscount)\
    \symbtrans \excst
  }
\end{mathpar}
We extend each rule of the concrete semantics to support such behaviors of symbolic
values.

>>>>

\section{Dynamic Shortcuts for JavaScript}\label{sec:javascript}
In this section, we introduce the core language of JavaScript that supports
first-class functions, open objects, and first-class property names, and define
{\sealed} execution of the core language for dynamic shortcuts.
Due to the space limitation, we present the main design of the
language in this paper and refer the interested readers to a companion report~\cite{report}.

@@

\subsection{{\SealeD} Execution}

We define the {\sealed} states by not only extending the concrete values
$\valset$ with {\sealed} values $\symbset$ but also adding the abstract counters
$\abscountset$ as follows:
\[
  \begin{array}{r@{~}c@{~}l}
    \symbstset &=& \labset \times \memset \times \ctxtset \times \eaddrset
    \times \abscountset\\
    \ctxtset &=& \eaddrset \finmap ((\eaddrset \times \labset \times \locset)
    \uplus \symbset)\\
    \valset &=& \pvalset \uplus \oaddrset \uplus \fvalset \uplus \symbset\\
    \abscountset &=& \oaddrset \rightarrow \{ \abszero, \absone, \absmany \}\\
  \end{array}
\]
Because JavaScript provides open objects, the properties of objects can be dynamically added or deleted.
Moreover, since object properties are string values that can be constructed at run time,
it is difficult to perform sound strong updates in static analysis.
To check the possibility of strong updates during {\sealed} execution,
we augment its states with the abstract counters $\abscountset$.

For each abstract value in a given abstract state,
if the abstract value denotes a single concrete value,
the converter $\asconverter: (\viewset \times
\absdom) \rightarrow (\absimapset \times \symbstset)$
keeps it; otherwise, $\asconverter$ replaces the abstract
value with its unique identifier and maintains the mapping from the
unique identifier to the abstract value to construct an abstract instantiation map.
The opposite converter $\saconverter: (\absimapset \times
  \symbstset)  \rightarrow (\viewset \times \absdom)$
recovers abstract values from their unique identifiers using the abstract instantiation map.
We define the {\sealed} transition relation $\symbtrans$
only if the next step does not require actual values of any {\sealed} values.
Otherwise, a given {\sealed} state does not have any {\sealed}
transitions to apply.  For example, we add the following rule for the $\kwret$ statement:
\begin{mathpar}
  \inferrule
  {
    \prog(\lab) = \kwret \; \expr\\
    \exprrule{\symbst}{\expr}{\val}\\
    \ctxt(\addr) \in \symbset
  }
  {
    \symbst = (\lab, \mem, \ctxt, \addr, \abscount)\
    \symbtrans \excst
  }
\end{mathpar}
We extend each rule of the concrete semantics to support such behaviors of {\sealed} 
values.

### 2021-02-24 paper/fse21/motivation.tex
Fixed typos.
Substituted "sealed symbolic" to "sealed" by using macro.

\paragraph{Dynamic shortcuts with concrete values.}
When a function is called with concrete values, we can perform
dynamic analysis instead of static analysis.
For example, \jscode{changeCountry} in Figure~\ref{fig:example}(b)
is invoked when a user selects a country from a drop-down list in the registration page.
It calls the \jscode{concat} function to update the drop-down list of
states or provinces on lines 17--18.  However, when the user selects ``United States of America,''
which is \jscode{"US"}, two arguments are pre-defined with
deterministic values; the first one is an array literal
\jscode{[["Other", "Other"]]} and the second one is an array of pairs
of abbreviations and names of the states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Moreover, \jscode{this} also has a concrete value, the Lodash top-level object \jscode{\_}.
Thus, we can perform dynamic analysis by invoking \jscode{concat} with
\jscode{\_} as its \jscode{this} value and the above concrete values as arguments. 
By skipping the analysis of the function call on lines 17--18 and
utilizing the result of dynamic analysis, it improved the analysis performance.

\begin{figure}[t]
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \top & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \symb_\jscode{int}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{this.pastEvents}}
    \label{fig:pastEvents}
  \end{subfigure}
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \jscode{0} & \symb_\jscode{evt}\\\hline
        \cdots & \cdots\\\hline
        \jscode{7} & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \jscode{8}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{e.events}}
    \label{fig:events}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Concrete objects with sealed symbolic values}
  \label{fig:sealed}
  \vspace*{-1em}
\end{figure}

\paragraph{Dynamic shortcuts with abstract values.}
Even when a function is called with abstract values, we can still
perform dynamic analysis using sealed symbolic execution.
For example, \jscode{getData} in Figure~\ref{fig:example}(c) is invoked
when a user clicks the ``Load More'' button to load more Zoom events in
the ``Webinars \& Events'' page.  It sends a POST
request to a server and receives additional events \jscode{e} on
line 24.  Then, eight events in \jscode{e.events} are appended to
\jscode{this.pastEvents} using \jscode{concat} on lines 27--28.
However, the arguments of \jscode{concat} are not deterministic because 1) the
event list stored in \jscode{this.pastEvents} is continuously grown for each
load and 2) the events stored in \jscode{e.events} are dependent on the
data given from the server.

To perform dynamic analysis with abstract values, we seal abstract values
with symbolic values as in Figure~\ref{fig:sealed}.  Two symbolic
values $\symbevt$ and $\symbint$ represent an event
object and an integer, respectively.  Then, we can perform dynamic analysis
successfully until line 9.  On line 2, \jscode{length} is \jscode{2};
on line 4, \jscode{array} points to \jscode{this.pastEvents};
on lines 5--8, \jscode{args} stores an array with a single object stored in \jscode{e.events};
and on line 9, \jscode{isArray(array)} is \jscode{true}.
However, dynamic analysis fails for \jscode{copyArray(array)} on line 10
because the value of the \jscode{length} property of \jscode{array} is the symbolic value $\symbint$.
Then, we stop the sealed symbolic execution, convert the current
sealed symbolic state to its corresponding abstract state, and resume
the static analysis from line 10.  Because sealed symbolic execution
leverages fast dynamic analysis as long as possible, the overall
analysis becomes more scalable.

\paragraph{Dynamic shortcuts for opaque functions.}
As the previous two examples additionally show, using dynamic shortcuts 
lessens the burden of modeling opaque functions from static analysis, and
it can even improve the analysis precision.
On line 9, since the \jscode{isArray} function is a JavaScript built-in library function,
it is implemented in a native language of the host environment, which
often requires manual modeling of its behaviors for JavaScript static analysis.
Assuming that a static analyzer models \jscode{isArray} to return the
boolean top value $\top_b$ that encompasses both \jscode{true} and \jscode{false},
static analysis of the ternary conditional expression on lines 9--10 analyzes
both branches \jscode{copyArray(array)} and \jscode{[array]}, even though
\jscode{[array]} is never reachable in the example code.  On the contrary,
using dynamic shortcuts, static analysis does not need to model \jscode{isArray}.
It can perform sealed symbolic execution for \jscode{isArray}, which
returns a more precise result \jscode{true} than $\top_b$.

>>>>

\paragraph{Dynamic shortcuts with concrete values.}
When a function is called with concrete values, we can perform
dynamic analysis instead of static analysis.
For example, \jscode{changeCountry} in Figure~\ref{fig:example}(b)
is invoked when a user selects a country from a drop-down list in the registration page.
It calls the \jscode{concat} function to update the drop-down list of
states or provinces on lines 16--17.  However, when the user selects ``United States of America,''
which is \jscode{"US"}, two arguments are pre-defined with
deterministic values; the first one is an array literal
\jscode{[["Other", "Other"]]} and the second one is an array of pairs
of abbreviations and names of the states defined as follows:
\begin{lstlisting}[style=myJSstyle,numbers=none]
WebinarBase.questions.state.items =
  [["AL","Alabama"], ..., ["WY", "Wyoming"]]
\end{lstlisting}
Moreover, \jscode{this} also has a concrete value, the Lodash top-level object \jscode{\_}.
Thus, we can perform dynamic analysis by invoking \jscode{concat} with
\jscode{\_} as its \jscode{this} value and the above concrete values as arguments. 
By skipping the analysis of the function call on lines 17--18 and
utilizing the result of dynamic analysis, it improved the analysis performance.

\begin{figure}[t]
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \top & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \symb_\jscode{int}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{this.pastEvents}}
    \label{fig:pastEvents}
  \end{subfigure}
  \begin{subfigure}{0.23\textwidth}
    \[
      \begin{array}{|c|c|}\hline
        \text{Property} & \text{Value}\\\hline
        \jscode{0} & \symb_\jscode{evt}\\\hline
        \cdots & \cdots\\\hline
        \jscode{7} & \symb_\jscode{evt}\\\hline
        \jscode{"length"} & \jscode{8}\\\hline
      \end{array}
    \]
    \vspace*{-1em}
    \caption{\jscode{e.events}}
    \label{fig:events}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Concrete objects with {\sealed} values}
  \label{fig:sealed}
  \vspace*{-1em}
\end{figure}

\paragraph{Dynamic shortcuts with abstract values.}
Even when a function is called with abstract values, we can still
perform dynamic analysis using {\sealed} execution.
For example, \jscode{getData} in Figure~\ref{fig:example}(c) is invoked
when a user clicks the ``Load More'' button to load more Zoom events in
the ``Webinars \& Events'' page.  It sends a POST
request to a server and receives additional events \jscode{e} on
line 24.  Then, eight events in \jscode{e.events} are appended to
\jscode{this.pastEvents} using \jscode{concat} on lines 27--28.
However, the arguments of \jscode{concat} are not deterministic because 1) the
event list stored in \jscode{this.pastEvents} is continuously grown for each
load and 2) the events stored in \jscode{e.events} are dependent on the
data given from the server.

To perform dynamic analysis with abstract values, we seal abstract values
with {\sealed} values as in Figure~\ref{fig:sealed}.  Two {\sealed}
values $\symbevt$ and $\symbint$ represent an event
object and an integer, respectively.  Then, we can perform dynamic analysis
successfully until line 9.  On line 2, \jscode{length} is \jscode{2};
on line 4, \jscode{array} points to \jscode{this.pastEvents};
on lines 5--8, \jscode{args} stores an array with a single object stored in \jscode{e.events};
and on line 9, \jscode{isArray(array)} is \jscode{true}.
However, dynamic analysis fails for \jscode{copyArray(array)} on line 10
because the value of the \jscode{length} property of \jscode{array} is the {\sealed} value $\symbint$.
Then, we stop the {\sealed} execution, convert the current
{\sealed} state to its corresponding abstract state, and resume
the static analysis from line 10.  Because {\sealed} execution
leverages fast dynamic analysis as long as possible, the overall
analysis becomes more scalable.

\paragraph{Dynamic shortcuts for opaque functions.}
As the previous two examples additionally show, using dynamic shortcuts 
lessens the burden of modeling opaque functions from static analysis, and
it can even improve the analysis precision.
On line 9, since the \jscode{isArray} function is a JavaScript built-in library function,
it is implemented in a native language of the host environment, which
often requires manual modeling of its behaviors for JavaScript static analysis.
Assuming that a static analyzer models \jscode{isArray} to return the
boolean top value $\top_b$ that encompasses both \jscode{true} and \jscode{false},
static analysis of the ternary conditional expression on lines 9--10 analyzes
both branches \jscode{copyArray(array)} and \jscode{[array]}, even though
\jscode{[array]} is never reachable in the example code.  On the contrary,
using dynamic shortcuts, static analysis does not need to model \jscode{isArray}.
It can perform {\sealed} execution for \jscode{isArray}, which
returns a more precise result \jscode{true} than $\top_b$.

### 2021-02-24 paper/fse21/related.tex
Substituted "sealed symbolic" to "sealed" by using macro.

\paragraph{Combined Analysis}
The most related previous work is combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.
They proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach has several
limitations compared with dynamic shortcuts.  First, it syntactically
divides a given program to \textit{applications} parts for static
analysis and \textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switch between static analysis and dynamic analysis.  It is
even impossible to perform both static and dynamic analysis of 
the same program part in different contexts.  In addition, while they
introduced \textit{mostly-concrete interpretation} similar to our
sealed symbolic execution, it supports only a special \textit{unknown}
value that represents any possible value.  Thus, it cannot preserve
the precision of complex abstract domains~\cite{revisit-recency,
  regex, weaklySPE} frequently used in JavaScript static analysis.
On the contrary, sealed symbolic execution automatically detects when
to switch to static analysis to use abstract semantics for abstract values.
Finally, \concerto\ preserves the soundness when a program satisfies
the \textit{state separation hypothesis}.  It assumes that the states
of application parts and framework parts are not interrogated
or manipulated by each other.  While the assumption may be reasonable
for static analysis of Java applications using external libraries, it
is not satisfied for JavaScript programs in general.  Unlike their
approach, our approach does not have any assumptions between static and
dynamic analysis parts.

>>>>

\paragraph{Combined Analysis}
The most related previous work is combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.
They proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach has several
limitations compared with dynamic shortcuts.  First, it syntactically
divides a given program to \textit{applications} parts for static
analysis and \textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switch between static analysis and dynamic analysis.  It is
even impossible to perform both static and dynamic analysis of 
the same program part in different contexts.  In addition, while they
introduced \textit{mostly-concrete interpretation} similar to our
{\sealed} execution, it supports only a special \textit{unknown}
value that represents any possible value.  Thus, it cannot preserve
the precision of complex abstract domains~\cite{revisit-recency,
  regex, weaklySPE} frequently used in JavaScript static analysis.
On the contrary, {\sealed} execution automatically detects when
to switch to static analysis to use abstract semantics for abstract values.
Finally, \concerto\ preserves the soundness when a program satisfies
the \textit{state separation hypothesis}.  It assumes that the states
of application parts and framework parts are not interrogated
or manipulated by each other.  While the assumption may be reasonable
for static analysis of Java applications using external libraries, it
is not satisfied for JavaScript programs in general.  Unlike their
approach, our approach does not have any assumptions between static and
dynamic analysis parts.
